Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
No aparecía el primer autor (arreglado)

\author{Juan-J.~Merelo, %Add your name here
  \thanks{JJ Merelo is with the Dept. of Computer Architecture and Technology and CITIC University of Granada
e-mail: (jmerelo@ugr.es).}
}% <-this % stops a space

\author{Mario Garcia-Valdez, %Add your name here
  \thanks{M Garcia-Valdez is with the Dept. of Graduate Studies at Instituto Tecnologico de Tijuana
e-mail: (mario@tectijuana.edu.mx).}
}% <-this % stops a space

>>>>

%  \author{Juan-J.~Merelo, %Add your name here
%  \thanks{JJ Merelo is with the Dept. of Computer Architecture and Technology and CITIC University of Granada
%  e-mail: (jmerelo@ugr.es).}
%  }% <-this % stops a space

%  \author{Mario Garcia-Valdez, %Add your name here
%    \thanks{M Garcia-Valdez is with the Dept. of Graduate Studies at Instituto Tecnologico de Tijuana
%  e-mail: (mario@tectijuana.edu.mx).}
%  }% <-this % stops a space

\author{Juan-J.~Merelo*$^1$, Mario Garcia-Valdez$^2$, Pedro A. Castillo$^1$
\thanks{Manuscript submitted for review on \today.}%
\thanks{$^1$Dept. of Computer Architecture and Technology and CITIC University of Granada}%
\thanks{$^2$Dept. of Graduate Studies at Instituto Tecnologico de Tijuana}%
\thanks{E-mail addresses: jmerelo@ugr.es , mario@tectijuana.edu.mx , pacv@ugr.es}%
\thanks{*Corresponding author.}%
}
